### 2019-04-26 monograph/thesis/chapters/beautifiers.tex
Removed the template monograph/thesis/postexto/apendice_a.tex
Added C language example for beautifiers.tex Application Fields.
Correções para linux

    \medskip
    % \begin{bluebox}
    \begin{enumerate}[nosep,nolistsep]
        \item Add new lines after `\{' and before `\}
        \item Add new lines before `\{'
        \item Remove empty lines
        \item Add comment lines before function
        \item Add new lines after `;'
        \item Add new lines after `\}'
        \item Remove new lines
        \item Reduce whitespace
        \item Fix bad indentation
    \end{enumerate}
    % \end{bluebox}
    \vspace{-4mm}\begin{flushright}\textcite{prettyPrinter}\end{flushright}

@@

    \url{https://github.com/r-lib/styler}
    \url{https://github.com/github/linguist}
    \url{https://forum.sublimetext.com/t/auto-align-symbolic/34375}
    \url{https://github.com/Thom1729/SmartIndent}
    \url{https://github.com/wbond/package_control_channel/issues/4310} Write a formatter utility

    With this ObjectBeautifier, we can edit XML files like YAML files, because
    the when we load the XML, we create a copy (the YAML version of the XML) on
    the `.object-beauty` folder which is edited by Sublime Text, and let the
    XML on its original place. Then when we save our YAML copy, we translate it
    to the XML original copy.
    \url{https://github.com/Microsoft/XmlNotepad}

>>>>

\medskip
% \begin{bluebox}
\begin{enumerate}[nosep,nolistsep]
    \item Add new lines after `\{' and before `\}
    \item Add new lines before `\{'
    \item Remove empty lines
    \item Add comment lines before function
    \item Add new lines after `;'
    \item Add new lines after `\}'
    \item Remove new lines
    \item Reduce whitespace
    \item Fix bad indentation
\end{enumerate}
% \end{bluebox}
\begin{flushright}\textcite{prettyPrinter}\end{flushright}

@@

\url{https://github.com/r-lib/styler}
\url{https://github.com/github/linguist}
\url{https://forum.sublimetext.com/t/auto-align-symbolic/34375}
\url{https://github.com/Thom1729/SmartIndent}
\url{https://github.com/wbond/package_control_channel/issues/4310} Write a formatter utility
\url{https://github.com/PyCQA/pydocstyle}
\url{https://github.com/PyCQA/pycodestyle}

\subsection{Configuration Detection}

If found on the project root folder,
a folder named `.object-beauty',
it will be used to store the automatically generated configurations based on the current configuration\s rules.
Such thing,
cannot be easily implemented because of the various complexities which can be introduced into the formatting rules.
For example,
the if configurations rules are simple and limited to just changing simple aspects of the formatting,
then the configuration generation will also be simple,
because there are only a few aspects to analyze.
However,
as the formatting rules grow up,
their complexity equally proportionally grows,
due the increased count of possibilities to analyze when combined together.

\subsection{Multidirectional Translation}

With this ObjectBeautifier,
we can edit XML files like YAML files,
because the when we load the XML,
we create a copy (the YAML version of the XML) on the `.object-beauty` folder which is edited by Sublime Text,
and let the XML on its original place.
Then when we save our YAML copy,
we translate it to the XML original copy.
Similarly,
for a C language code,
it would be like to change some bit on the compiled binary code and have the change reflected on the original C source code.
\url{https://github.com/Microsoft/XmlNotepad}

Open Source Neural Machine Translation in Torch,
translates between languages by machine learning.
\url{https://github.com/OpenNMT/OpenNMT}

### 2019-04-26 monograph/thesis/chapters/object_beautifier.tex
Correções para linux

@@

This program class is commonly know as text formatters.
The differential from this work from others is the goal of a single expandable tool,
capable of manipulating all existent and future programming languages,
based on the use of deterministic \cite{TODO:
deterministic free grammars explanation} and controlled nondeterministic \cite{TODO:
section explaning what does controlled means} context free grammars.

This audacious goal,
can only be accomplished because the proposed tool does not rely on the lex,
syntax and semantic aspects \cite{TODO:
what does these languages aspects are} of any used languages.
Therefore,
it is up to this tool users\s to write the lex and syntactic,
but they are not required to write the semantic aspects of the desired language,
as the objective of text formatters is to change the structural aspects \cite{TODO:
what are the source code formatters objectives}.

.sublime-syntax or my .object-beauty is a meta-language, as EBNF \cite{Extended Backus–Naur form}.

@@

// Defines a expression which will map the ending of a exclusion block.
Scope End:
\\\*
\end{lstlisting}
\vspace*{-4mm}

>>>>

Para processar a árvore de sintática, é necessário iterar várias vezes pela árvore, que novos escopos não sejam mais aplicados.
Por exemplo,
\begin{lstlisting}
pawn_string: {
  match: " {
    scope: punctuation.definition.string.begin.sma
    push: {
      meta_scope: string.quoted.double.sma
      match: " {
        scope: punctuation.definition.string.end.sma
        pop: true
      }
    }
  }
}
\end{lstlisting}
Essa gramática é válida para reconhecer strings, mas se pegar a primeira expressão
regular e fizer um findall(), eu também vou retornar o fechamento da string.
Assim, quando eu chegar no fecha aspas, ele já vai está consumido.

@@

This program class is commonly know as text formatters.
The differential from this work from others is the goal of a single expandable tool,
capable of manipulating all existent and future programming languages,
based on the use of deterministic
% TODO:\cite{deterministic free grammars explanation}
and controlled nondeterministic
% \cite{TODO:section explaning what does controlled means}
context free grammars.

This audacious goal,
can only be accomplished because the proposed tool does not rely on the lex,
syntax and semantic aspects
% \cite{TODO:what does these languages aspects are}
of any used languages.
Therefore,
it is up to this tool users\s to write the lex and syntactic,
but they are not required to write the semantic aspects of the desired language,
as the objective of text formatters is to change the structural aspects
% \cite{TODO:what are the source code formatters objectives}
.

.sublime-syntax or my .object-beauty is a meta-language, as EBNF
% TODO: \cite{Extended Backus–Naur form}.

@@

// Defines a expression which will map the ending of a exclusion block.
Scope End:
\\\*
\end{lstlisting}
